---
title: "Supplemental Results to Accompany Approach-Avoid RLWM Paper"    
date: "`r Sys.Date()`"
author: "Peter Frank Hitchcock - Translational Lab, Emory University"
output:
  html_document:
    toc: true
---

# Set up packages, function sourcing, and plotting parameters   

```{r, results='hide'}
sapply(c(
         "rjson", 
         "data.table", 
         "dplyr", 
         "ggplot2", 
         "stringr", 
         "purrr", 
         "foreach", 
         "patchwork", 
         "testit",
         "lme4", 
         "lmerTest", 
         "latex2exp"
         ), 
       require, character=TRUE)
sf <- function() invisible(sapply(paste0("./Functions/", list.files("./Functions/", recursive=TRUE)), source)) # Source all fxs
sf()
DefPlotPars()
```

# Behavioral data  

Read in learn and test df, questionnaires, and demographics  
```{r}
learn_df <- read.csv("../data/learn_df.csv")
test_df <- read.csv("../data/test_df.csv")
```

Exclude from further analyses the pt who failed both catch qs     

```{r}
# qdf %>% filter(catch_q_1 != 1) %>% select(ID)
# qdf %>% filter(catch_q_2 != 1) %>% select(ID)
qdf <- read.csv("../data/questionnaire_df.csv")
demogs <- read.csv("../data/demogs_deident.csv")
if (all(demogs$ID==qdf$ID)) qdf$group <- demogs$group
qdf <- qdf %>% filter(!ID==255)
demogs <- demogs %>% filter(!ID==255)
learn_df <- learn_df %>% filter(!ID==255)
test_df <- test_df %>% filter(!ID==255)
```

Create sum scores  

```{r}
qdf$BDI_sum <- rowSums(qdf %>% select(contains(c("BDI"))), na.rm=TRUE)
qdf$GAD_sum <- rowSums(qdf %>% select(contains(c("GAD"))), na.rm=TRUE)
qdf$RRS_sum <- rowSums(qdf %>% select(contains(c("RRS"))), na.rm=TRUE)
```

```{r}
qdf$depr_anx_sum <- qdf$BDI_sum + qdf$GAD_sum
```


Get model sims  

```{r}
m35_s <- 
  read.csv("../model_res/sims/SIM_RunRLWMPRew53679.csv")
```

```{r}
length(unique(m35_s$iter)) 
```

```{r}
m35_s_learn <- m35_s %>% filter(type=="learning")
m35_s_test <- m35_s %>% filter(type=="test")
```


# Parameter recovery  

```{r}
m35_pr <- read.csv("../model_res/par_recov/pr_res/par_recov_BEST__RunRLWMPRew_85741.csv") # 8/1/24 with minor bug correction  
```


```{r}
p1 <- ComparePars(m35_pr$kappa_simmed, m35_pr$kappa_recovered, TeX('$\\kappa'))
p2 <- ComparePars(m35_pr$phi_simmed, m35_pr$phi_recovered, TeX('$\\phi'))
p3 <- ComparePars(m35_pr$rho_simmed, m35_pr$rho_recovered, TeX('$\\rho'))
p4 <- ComparePars(m35_pr$alpha_pos_simmed, m35_pr$alpha_pos_recovered, TeX('$\\alpha_{+}')) + 
  theme(axis.text = element_text(size=11))
p5 <- ComparePars(m35_pr$alpha_neg_simmed, m35_pr$alpha_neg_recovered, TeX('$\\alpha_{-}')) + 
  theme(axis.text = element_text(size=11))
p6 <- ComparePars(m35_pr$rl_off_simmed, m35_pr$rl_off_recovered, TeX('$\\RL^{off}'))+ 
  theme(axis.text = element_text(size=11))
p7 <- ComparePars(m35_pr$not_pun_bonus_simmed, m35_pr$not_pun_bonus_recovered, TeX('$\\non-pun_{bonus}')) 
p8 <- ComparePars(m35_pr$epsilon_simmed, m35_pr$epsilon_recovered, TeX('$\\epsilon'))+ 
  theme(axis.text = element_text(size=11))
wm_pars <- p1 + p2 + p3
rl_pars <- p4 + p5 + p6
other_pars <- p7 + p8 + p6
```


```{r}
# ComparePars(m35_pr$not_pun_bonus_simmed, m35_pr$not_pun_bonus_recovered, TeX('$\\non-pun_{bonus}'), "Simulated", "Recovered")
```

```{r, fig.width=11, fig.height=4.5}
wm_pars
```
```{r, fig.width=11, fig.height=4.5}
rl_pars
```

```{r, fig.width=11, fig.height=4.5}
other_pars # RL off again just for balance in figure - cropped for paper fig 
```

```{r}
#ggsave("../paper/figs/pieces/par_recov_part1.png", wm_pars, height = 4.5, width=11, dpi=300)
#ggsave("../paper/figs/pieces/par_recov_part2.png", rl_pars, height = 4.5, width=11, dpi=300)
#ggsave("../paper/figs/pieces/par_recov_part3.png", other_pars, height = 4.5, width=11, dpi=300)
```


Check recovery of median split  


```{r}
# Code which of the simulated parameters are above the simmed median  
m35_pr$simmed_above_median <- (m35_pr$rl_off_simmed > median(m35_pr$rl_off_simmed))*1
# Code which of the recovered pars above the median 
m35_pr$recovered_above_median <- (m35_pr$rl_off_recovered > median(m35_pr$rl_off_recovered))*1
```

How often do are the true pars above the median above the median in the recovered data?  

```{r}
table(m35_pr$simmed_above_median==m35_pr$recovered_above_median)
```

```{r}
table(m35_pr$simmed_above_median==m35_pr$recovered_above_median)[2]/sum(table(m35_pr$simmed_above_median==m35_pr$recovered_above_median))
```

## Simulations of RL off  

```{r}
m35 <- read.csv("../model_res/opt/best/BEST__m35_RunRLWMPRew-8-1-24-epsilonfixed.csv") # the final model with the bug/nonsensical implementation of epsilon fixed on 8/1
```



```{r}
# Divide participants into low vs. high RL off groups  
little_coop <- data.frame(m35 %>% filter(rl_off <= median(m35$rl_off)))$ID
high_coop <- data.frame(m35 %>% filter(rl_off > median(m35$rl_off)))$ID
```

## Simulation predictions for high vs. low blunting  

Add SI6 to this and move to supplemental  

```{r}
# Divide participants into low vs. high RL off groups  
little_coop <- data.frame(m35 %>% filter(rl_off <= median(m35$rl_off)))$ID
high_coop <- data.frame(m35 %>% filter(rl_off > median(m35$rl_off)))$ID
```


```{r}
p1_test_sim_trials_m35_lc <- m35_s_test %>% filter(phase==1 & ID %in% little_coop)
pcor_p1_test_sim_m35_lc <- 
  data.frame(p1_test_sim_trials_m35_lc %>% group_by(set_size) %>% summarize(m=mean(corrects)))

pcor_sim_m35_si6_lc <- 
  data.frame(m35_s_learn %>% filter(stim_iter==6  & ID %in% little_coop) %>% group_by(set_size) %>% summarize(m=mean(corrects)))

p2_test_sim_trials_m35_lc <- m35_s_test %>% filter(phase==2 & ID %in% little_coop)
pcor_p2_test_sim_m35_lc <- 
  data.frame(p2_test_sim_trials_m35_lc %>% group_by(set_size) %>% summarize(m=mean(corrects)))

sim_p1_test_m35_lc <- ggplot(pcor_p1_test_sim_m35_lc, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + 
  tp + ggtitle("Sim phase 1 test - \n little RPE blunting")

pcor_sim_m35_si6_lc <- ggplot(pcor_sim_m35_si6_lc, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + 
  tp + ggtitle("Sim stim iter 6 \n low RPE blunting")

sim_p2_test_m35_lc <- ggplot(pcor_p2_test_sim_m35_lc, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + tp +
  tp + ggtitle("Sim phase 2 test - \n little RPE blunting")
```


```{r}
p1_test_sim_trials_m35_hc <- m35_s_test %>% filter(phase==1 & ID %in% high_coop)
pcor_p1_test_sim_m35_hc <- 
  data.frame(p1_test_sim_trials_m35_hc %>% group_by(set_size) %>% summarize(m=mean(corrects)))
p2_test_sim_trials_m35_hc <- m35_s_test %>% filter(phase==2 & ID %in% high_coop)
pcor_p2_test_sim_m35_hc <- 
  data.frame(p2_test_sim_trials_m35_hc %>% group_by(set_size) %>% summarize(m=mean(corrects)))

pcor_sim_m35_si6_hc <- 
  data.frame(m35_s_learn %>% filter(stim_iter==6  & ID %in% high_coop) %>% group_by(set_size) %>% summarize(m=mean(corrects)))


sim_p1_test_m35_hc <- ggplot(pcor_p1_test_sim_m35_hc, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + 
  tp + ggtitle("Sim phase 1 test \n high RPE blunting")

pcor_sim_m35_si6_hc <- ggplot(pcor_sim_m35_si6_hc, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + 
  tp + ggtitle("Sim stim iter 6 \n high RPE blunting")

sim_p2_test_m35_hc <- ggplot(pcor_p2_test_sim_m35_hc, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + tp +
  tp + ggtitle("Sim phase 2 test \n high RPE blunting")
```
  
  
And indeed, the model predicts that those with little RPE blunting will have the best performance at set size 2... 

```{r, fig.height=5, fig.width=11}
sim_p1_test_m35_lc + pcor_sim_m35_si6_lc + sim_p2_test_m35_lc
```
... whereas those with higher blunting will have the best performance at later set sizes   

```{r, fig.height=5, fig.width=11}
sim_p1_test_m35_hc + pcor_sim_m35_si6_hc + sim_p2_test_m35_hc
```


## Effect of lesioning RL off  

```{r}
m35_s_lesion_rloff <- 
  read.csv("../model_res/sims/SIM_RunRLWMPRewLesionRLOff14495.csv")
m35_s_lesion_rlofftomax <- 
  read.csv("../model_res/sims/SIM_RunRLWMPRewRLOffToMax39938.csv")
```


```{r}
m35_s_lrl_si6 <- m35_s_lesion_rloff %>% filter(type=="learning", stim_iter==6)
m35_s_lrl_test <- m35_s_lesion_rloff %>% filter(type=="test")
m35_s_lrlmax_si6 <- m35_s_lesion_rlofftomax %>% filter(type=="learning", stim_iter==6)
m35_s_lrlmax_test <- m35_s_lesion_rlofftomax %>% filter(type=="test")
```

```{r}
pcor_si6_sim_m35_lrl <- 
  data.frame(m35_s_lrl_si6  %>% group_by(set_size) %>% summarize(m=mean(corrects)))

p1_test_sim_m35_lrl <- 
  data.frame(m35_s_lrl_test %>% filter(phase==1) %>%  group_by(set_size) %>% summarize(m=mean(corrects)))

p2_test_sim_m35_lrl <- 
  data.frame(m35_s_lrl_test %>% filter(phase==2) %>%  group_by(set_size) %>% summarize(m=mean(corrects)))

sim_p1_si6_lrl <- ggplot(pcor_si6_sim_m35_lrl, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + 
  tp + ggtitle("Sim stim iter 6 \n Lesion RL off")

sim_p1_test_lrl <- ggplot(p1_test_sim_m35_lrl, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + tp +
  tp + ggtitle("Sim phase 1 test \n Lesion RL off")

sim_p2_test_lrl <- ggplot(p2_test_sim_m35_lrl, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + tp +
  tp + ggtitle("Sim phase 2 test \n Lesion RL off")

```

```{r}
pcor_si6_sim_m35_lrlmax <- 
  data.frame(m35_s_lrlmax_si6  %>% group_by(set_size) %>% summarize(m=mean(corrects)))

p1_test_sim_m35_lrlmax <- 
  data.frame(m35_s_lrlmax_test %>% filter(phase==1) %>%  group_by(set_size) %>% summarize(m=mean(corrects)))

p2_test_sim_m35_lrlmax <- 
  data.frame(m35_s_lrlmax_test %>% filter(phase==2) %>%  group_by(set_size) %>% summarize(m=mean(corrects)))

sim_p1_si6_lrlmax <- ggplot(pcor_si6_sim_m35_lrlmax, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + 
  tp + ggtitle("Sim stim iter 6 \n RL off to max ")

sim_p1_test_lrlmax <- ggplot(p1_test_sim_m35_lrlmax, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + tp +
  tp + ggtitle("Sim phase 1 test \n RL off to max")

sim_p2_test_lrlmax <- ggplot(p2_test_sim_m35_lrlmax, aes(x=as.factor(set_size), y=m, fill=as.factor(set_size))) + 
  geom_hline(yintercept = seq(.1, 1, .1), alpha=.3) +
  geom_bar(stat="identity", color="black") +
  ga + ap + xlab("Set size") + ylab("Proportion correct") + tol + ylim(0, 1) + tp +
  tp + ggtitle("Sim phase 2 test \n RL off to max")

```

```{r, fig.height=5, fig.width=11}
sim_p1_test_lrl + sim_p1_si6_lrl + sim_p2_test_lrl 
```

```{r, fig.height=5, fig.width=11}
sim_p1_test_lrlmax + sim_p1_si6_lrlmax + sim_p2_test_lrlmax
```


For WM-SR model results see other notebook  
